\documentclass[]{article}
\usepackage{url}
\usepackage[margin=1in]{geometry}
\usepackage{titling}

\title{Mr Hadleigh Thompson}
\author{BSc Atmospheric Science\\ 
Ph: 1-(613)-316-4679 \\
Email: hadleighthompson@gmail.com \\
Web: hadleigh.github.io}
\date{October 2016}

\pretitle{\begin{flushright}\LARGE}
\posttitle{\end{flushright}}
\preauthor{\begin{flushright}\large}
\postauthor{\end{flushright}}
\predate{\begin{flushright}\large}
\postdate{\end{flushright}}

\begin{document}
\maketitle
\vspace{10mm}

\section*{\underline{Objective:}}  
To develop and utilize the meteorological theory and tools provided my Atmospheric Science degree. I hope in the future to combine these with my interest and knowledge of outdoor activities and pursuits, and research in wilderness locations. 

\section*{\underline{Relevant Education:}}
\subsubsection*{University of British Columbia (UBC), Vancouver 2014 - 2016}
Completion of a Bachelor of Science degree – with a major in Atmospheric Science. Main
interests include: mountain and cold region meteorology, snow and ice thermodynamics,
hydrometeorology, and avalanche phenomena.
\subsubsection*{Thompson Rivers University (TRU), Kamloops 2012 - 2014}
Pre-requisites and lower level Bachelor of Science courses – aiming for admittance to University of British
Columbia.
\subsubsection*{Canadian Avalanche Association (CAA), British Columbia 2010 - 2012}
Member since 2009. Introduction and Advanced ‘Weather for Avalanche workers’ – 5 days total. Avalanche Operations, Level One – 7 days.

\section*{\underline{Employable Skills:}}
\subsubsection*{Technical}
\begin{itemize}
\item Operational Meteorological forecasting - As demonstrated throughout UBC Atmospheric science degree.
\item Python coding and Numerical modelling - extensive academic experience in writing Python code to solve problems in Atmospheric and Earth sciences.
\item Github workflow and collaboration in an academic environment.
\item Self-taught webpage design and HTML scripting - see \url{http://hadleigh.github.io}
\item GIS workflow and operation using QGIS
\item Linux environment and command line computational operations.
\item High level of numerical modelling and mathematical analysis using matlab, python, iPython notebooks, and Pandas data-frames.
\end{itemize}
\subsubsection*{Practical}
\begin{itemize}
\item Comfortable in wide range of outdoor environments including wilderness work-sites. 
\item Organizational and logistical skills obtained from both military experience and adventure tourism company management.
%\item Operational skills include: boat handling; travelling in mountainous terrain in all seasons; working on ocean going vessels; experience with heavy machinery; comfortable operating alternative transportation such as buses, ATVs, and snowmobiles.  
\item Ability to adapt and solve practical problems with limit resources.
%\item Extensive experience in working in marginal and difficult operational conditions.
\end{itemize}

\section*{\underline{Relevant Experience:}}
\subsubsection*{OWL Rafting on the Ottawa River. Ontario Canada – Operations Manager: 2010 - Present}
Managing logistics and maintenance personnel. Operational Health and Safety. Boat (flat-water and swift water) and vehicle operation. Bus driving. Expenditure accounting and department financial responsibility.
\subsubsection*{Mustang Powder Cats. British Columbia Canada – Tail-guide Practicum program: Winter 2009/2010}
Lodge and operation maintenance. Guest safety and assistance while skiing. Collection of near surface weather observations. Snowpack profile analysis and recording. Avalanche observation and investigation. 
 \subsubsection*{Franz Josef Glacier. New Zealand – Glacier Guide: 2008 - 2009}
Leading guests on Glacier hikes. Helicopter loading. Ice climbing instruction. Crevasse extraction. Alpine
cliff rescue team member.
\subsubsection*{Fernie Alpine Resort, British Columbia. Canada – Ski Patrol team member: 2007 - 2008}
Guest liaison, information, and assistance. First aid and emergency response. Avalanche control. Near surface weather observations. Avalanche and snowpack investigations and recording. Snow blasting.
\subsubsection*{Collets Mountain Holidays, Central Dolomites. Italy – Hiking Guide: 2005 - 2007}
Summer hiking and via ferrata; Winter snowshoeing and cross-country skiing. Personnel and chalet management. Expenditure accounting and recording. Chalet operations and management.
\subsubsection*{Royal New Zealand Army Medical Corps. New Zealand – Field and Surgical team medic: 1997 - 2003}
2 years in-house medical, first aid, and emergency response training. 3 years operational service including 3 overseas deployments; UN sanctioned peacekeeping missions.

\section*{\underline{Additional Skills:}}
\begin{itemize}
\item Full drivers license, including passenger Bus (Ontario)
\item Transport Canada 'Limited Master' certificate
\item Work place first aid and CPR certified
\item Previous field research work and experience with Oxford University Ecology Department, (Summer 2003, 2004)
%\item Canadian Ski instructors alliance level 2 certified
\end{itemize}

\section*{\underline{Contact Details:}}
\begin{itemize}
\item Email: hadleighthompson@gmail.com
\item Ph: 1 (613) 316-4679
\item Current postal address: 763 Sussex Blvd, Kingston. ON K7M 5B4.
\end{itemize}

%\section*{\underline{References:}}
%\begin{itemize}
%\item Forecasting Experience:\\
%David Siuta \\
%Course Instructor - ATSC 406, Synoptic Meteorology and Forecasting \\
%Atmospheric Science \\
%University of British Columbia\\
%email: dsiuta@eos.ubc.ca
%\item Academic: \\ 
%Dr Phil Austin \\
%Atmospheric Science Head of Department \\
%Earth, Ocean, and Atmospheric Sciences \\
%University of British Columbia \\
%email: paustin@eos.ubc.ca
%\item Employment: \\
%Dirk Van Wijk \\
%Owner, Owl Rafting on the Ottawa River \\
%Foresters Falls, ON. Canada. \\
%email: raft@owl-mkc.ca
%\end{itemize}

\end{document}
